---
title: "DC Notes: ML Toolbox with Caret"
author: "`r Sys.getenv('USERNAME')`"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
## basic settings
knitr::opts_chunk$set(echo = FALSE,
                      message=FALSE,
                      warning=FALSE
                      )

## load common libraries
library(tidyverse)
library(lubridate)
library(scales)
library(plotly)
library(PerformanceAnalytics)
library(caret)

## Reference: R Markdown cheatsheet
## https://www.rstudio.com/wp-content/uploads/2016/03/rmarkdown-cheatsheet-2.0.pdf

```

## Intro {.tabset}

* caret is one of the most popular R pkgs for supervised learning (aka predictive modeling)
* used when you have a specific target variable to predict
* two main types of supervised learning:
    + Regression -> quantitative (size, amount, etc)
    + Classification -> qualitative (categories, status, etc)
* RMSE for model performance evaluation
    + calc on 'out of sample' data, not data used for modeling ('in-sample')
    + helps reduce over-fitting
    + still need to calc in-sample RMSE to see how model performs on sample data and then compare with out-of-sample

### Regression Models: fitting and evaluating

```{r reg 1}

```


